\chapter{References}

\section{Sources}

\begin{itemize}
\item Source 1- Dimethyl ether, diethyl ether and ethylene from alcohols - Aysegul Ciftci a, Dilek Varisli b, Kenan Cem Tokay a, N. Aslı Sezgi a, Timur Dogu a - "Dimethyl ether, diethyl ether \& ethylene from alcohols over tungstophosphoric acid based mesoporous catalysts" - Accessed 17:45, 09/02/2015.

\item Source 2 - The Ideal Gas Equation - \url{http://www.chemguide.co.uk/physical/kt/idealgases.html} - Accessed 18:32, 09/02/2015.

\item Source 3 - The Thermite Reaction - \url{http://www.rsc.org/Education/EiC/issues/2011January/ExhibitionChemistry.asp?e=1} - Accessed 18:20, 09/02/2015.

\item Source 4 - Catalysis in Industry - \url{http://www.essentialchemicalindustry.org/processes/catalysis-in-industry.html} - Accessed 18:45, 09/02/2015.

\item Source 5 - Ik-Hwan Um, Young-Min Park, and Eun-Hee Shin - "The Effect of Solvent on Reaction Rates and Equilibria for the Reactions of
p-Nitrophenyl Acetate with Alicyclic Secondary Amines in H2O and DMSO" - Accessed 11:11 10/02/2015.

\item Source 6 - S. Pancharatnam, R. A. Huggins and D. M. Mason - "Catalytic Decomposition of Nitric Oxide on Zirconia by Electrolytic Removal of Oxygen" - Accessed 12:06 10/02/2015.

\item Source 7  - Average and Instantaneous Rates - \url{http://chemwiki.ucdavis.edu/Physical_Chemistry/Kinetics/Reaction_Rates/Measuring_Reaction_Rates} - Accessed 16:23, 09/02/2015.

\item Source 8 - Acid Properies - \url{http://chemwiki.ucdavis.edu/Physical_Chemistry/Acids_and_Bases/Acid} - Accessed 17:59, 10/02/2015.

\item Source 9 - Louise Lerner - "7 things you may not know about catalysis" - Accessed 18:39, 10/02/2015.

\item Source 10 - Catalyst - \url{http://goldbook.iupac.org/C00876.html} - Accessed 21:25, 11/02/2015.

\item Source 11 - Kinetics Part 1 - \url{http://www.docbrown.info/page03/ASA2rates.htm} - Accessed 10:16, 12/02/2015.

\item Source 12 - Electrolytic Cells - \url{http://ilovechemistry92.blogspot.co.uk/2011/02/difference-between-electrochemical-cell.html} - Accessed 16:40, 01/03/2015.

\item Source 14 - Electrochemical Catalyst - \url{http://chem.lapeer.org/Chem1Docs/ElectChemCat.html} - Accessed 16:46, 01/03/2015.

\item Source 15 - Octahedral Molecular Geometry - \url{http://en.wikipedia.org/wiki/Octahedral_molecular_geometry} - Accessed 20:34, 03/03/2015.

\item Source 16 - Paramagnetism - \url{http://www.britannica.com/EBchecked/topic/442927/paramagnetism} - Accessed 20:36, 03/03/2015.





\end{itemize}





\section{Figures}
\begin{itemize}

\item Figure 2.1 - Zero-Order Rate vs Concentration Graph - \url{http://ibchem.com/IB/ibnotes/16.1.htm} - Accessed 17:24, 10/02/2015.

\item Figure 2.2 - First-Order Rate vs Concentration Graph  - \url{http://ibchem.com/IB/ibnotes/16.1.htm} - Accessed 17:24, 10/02/2015.

\item Figure 2.3 - Second-Order Rate vs Concentration Graph  - \url{http://ibchem.com/IB/ibnotes/16.1.htm} - Accessed 17:24, 10/02/2015.

\item Figure 2.4 - pH Scale - \url{http://www.heartupdate.com/prevention/ph-body-influence-daily-life_94/} - Accessed 13:01, 09/02/2015. 

\item Figure 2.5 - Ben Keppie Table - Table made from information from: Foster, Laurence S. and Irving J. Gruntfest, "Demonstration Experiments Using Universal Indicators", J. Chem. Ed., 14, 274 (1937).

\item Figure 2.6 - D-Orbitals - \url{http://www.chemeddl.org/resources/TSTS/Stahl/Stahl9-12/Orbitals9to12.html} - Accessed 12:37, 11/02/2015.

\item Figure 2.7 - Copper Ion d Orbital Representation - \url{http://www.chemguide.co.uk/inorganic/complexions/whatis.html} - Accessed 9:18, 24/03/2015.

\item Figure 2.8 - Complex Shapes and Structures - \url{http://www.docbrown.info/page07/appendixtrans03.htm} - Accessed 14:49, 11/02/2015.


\item Figure 2.9 - Exothermic Enthalpy Diagram - \url{http://awkwardrevision.weebly.com/enthalpy.html} - Accessed 16:21, 11/02/2015.

\item Figure 2.10 - Endothemic Enthalpy Diagram - \url{http://awkwardrevision.weebly.com/enthalpy.html} - Accessed 16:21, 11/02/2015.

\item Figure 2.11 - Gas Syringe Experiment - \url{http://www.bbc.co.uk/schools/gcsebitesize/science/add_ocr_gateway/chemical_economics/reaction1rev1.shtml} - Accessed 14:20, 09/02/2015.

\item Figure 2.12 - Inverted Burette Experiment - \url{http://www.uq.edu.au/_School_Science_Lessons/17.1.2ch.GIF} - Accessed 20:08, 03/03/2015.

\item Figure 2.13 - Mass Change Experiment - \url{http://everythingmaths.co.za/science/grade-12/07-rate-and-extent-of-reaction/07-rate-and-extent-of-reaction-03.cnxmlplus} - Accessed 15:19, 09/02/2015.



\item *All other figures are made solely from my own data which I gathered by the experimental methods of this coursework*









\end{itemize}